\documentclass{ExpressiveResume}

\begin{document}

%--------------------------------------------------------------------------------------%
\resumeheader[
    firstname=              Doruk Tan,
    middleinitial=          ,
    lastname=               Atila,
    email=                  doruktanatila4@gmail.com,
    phone=                  773-313-1169,
    linkedin=               doruktanatila,
    github=                 ProfDorukTan,
    city=                   Manchester,
    state=                  UK,
    qrcode=                 ./images/Linkedin_QR.png,
    fixobjectivespacing=    true
]


%--------------------------------------------------------------------------------------%
\objective{Final year electronic engineering student with 4.0 GPA, various projects and research experiences. \\
    Passionate about \tech{computer architectures} (digital/analog), \tech{embedded
        systems} and \tech{materials science} with a niche interest in \tech{neuromorphic
        computing}. Seeking full-time opportunities in these fields.}


%--------------------------------------------------------------------------------------%
\section{Education}

\experience{Bachelor of Engineering}{Electronic Engineering}{Sept 2021}{June 2024}{
    \noindent The University of Manchester, Manchester, UK \hfill 1st Class Honours
    \achievement{Relevant coursework: Microelectronic Components, Digital System
        Design, Computer Systems Architecture, VLSI Design, C Programming,
        Microcontroller Engineering 1\&2, Embedded Systems}
}
\experienceAlternative{High School Diploma}{Sept 2016}{June 2021}{
    \noindent The American Robert College of Istanbul, Turkey \hfill GPA: 88.03/100 \newline}


%--------------------------------------------------------------------------------------%
\section{Work Experience}

\experience{Data Analyst/Business Developer}{Arcanor - Istanbul, Turkey}{May 2022}{June 2023}{
    \achievement{
        Optimized SQL queries and developed an algorithm to query cross-country mobility data
    }
    \achievement{
        Coordinated various tasks as part of a startup team,
        working extensively in product development, documentation, website
        management, Google services,
        translation
    }
    \achievement{
        Skills: \tech{Data Analysis}, \tech{Project Management}, \tech{SQL},
        \tech{Startup Management}, \tech{Google Services}
    }
}
\experience{Intern}{Softtech Software Technologies R\&D - Istanbul, Turkey}{June 2019}{July 2019}{
    \achievement{
        Wrote and implemented a Python code for automated and manual drone controlling
    }
    \achievement{
        Trained a pattern recognition algorithm in Python to identify a
        medical disease with software development team members
    }
    \achievement{
        Skills: \tech{Simulation}, \tech{Linux - Ubuntu}, \tech{Embedded
            Systems}, \tech{Python}, \tech{Machine Learning} \newline
    }
}


%--------------------------------------------------------------------------------------%
\section{Publications}

\publicationInProgress{Designing Low-power, Non-invasive, Conformable,
    Organic Field Effect Transistor-based Sensors Using Natural Dielectric
    Polymers and Novel Organic Semiconductors and Their Characterizations}
{2024}{Status: Experiments - expected to be published in late 2024}{
    \achievement{
        Skills: \tech{Research}, \tech{Electrical Characterizations}, \tech{Materials Science}, \tech{Organic
            Electronics}, \tech{Spin-coating}, \tech{PVD}, \tech{OFET}
    }
}
\publicationInProgress{A Novel Approach to Modelling of MOS Devices – Development of a Simulation Tool for MOSFET Analysis}
{2024}{Available in GitHub}{
    \achievement{
        Undergraduate final year dissertation project
    }
    \achievement{
        Skills: \tech{MOSFET}, \tech{Modelling}, \tech{Solid State Physics}, \tech{Simulation}, \tech{C++}
    }
}
\publicationInProgress{“Organic phototransistors and their applications as artificial synapses,” Sens Actuators A Phys, vol. 371, p. 115311, 2024, doi: https://doi.org/10.1016/j.sna.2024.115311.}
{2024}{Published in Sensors and Actuators A: Physical}{
    \achievement{
        Skills: \tech{Research}, \tech{Materials Science}, \tech{Organic
            Electronics}, \tech{Artificial Synapses}, \tech{Neuromorphic Computing},
        \tech{Spin-coating}, \tech{PVD}, \tech{OFET} \newline
    }
}


%--------------------------------------------------------------------------------------%
\section{Projects}

\experience{MOSFET Modelling and Simulation}{Undergraduate Final Year
    Project}{Sept 2023}{May 2024}{
    \achievement{
        Derived a MOSFET model from quantum-mechanical semiconductor physics
        foundations and built a standalone C++ program capable of simulating the
        output and transfer curves of a MOSFET with manufacturing parameters.
    }
    \achievement{
        Skills: \tech{C++}, \tech{Qt}, \tech{MOSFET}, \tech{Solid State Physics}, \tech{Modeling},
        \tech{Simulation}, \tech{Semiconductor Device}, \tech{OFET}
    }
}
\experience{Concurrent Systems}{Coursework Assignment}{Nov 2023}{Nov 2023}{
    \achievement{
        Coded a simulation of a four-by-one hundred-meter sprint relay race.
        The project involved creating threads, synchronizing threads, and
        ensuring thread safety.
    }
    \achievement{
        Skills: \tech{C++}, \tech{Multithreading}
    }
}
\experience{Microcontroller-Peripheral Communication I2C/SPI}{Coursework Assignment}{Nov 2023}{Nov 2023}{
    \achievement{
        Programmed STM32F401RE microcontroller using low-layer C
        libraries to enable data transfer between the controller and
        peripherals.
    }
    \achievement{
        Skills: \tech{Embedded Systems}, \tech{C}, \tech{SPI}, \tech{I2C}, \tech{Keil uVision}
    }
}
\experience{Line Following Buggy}{Embedded Systems Project}{Sep 2022}{June 2023}{
    \achievement{
        Programmed STM32F401RE microcontroller to create a
        line-following buggy. The system gathered data from six light sensors, determined the
        line's position, and adjusted the motor speed to center the line
        using PID control.
    }
    \achievement{
        Skills: \tech{Embedded Systems}, \tech{C++}, \tech{STM32}, \tech{Algorithms}
    }
}
\experience{VLSI Design}{Coursework}{May 2023}{May 2023}{
    \achievement{
        Designed a 250nm technology CMOS schematic and layout of a circuit.
        Optimized the circuit for given speed/power requirements and passed
        DRC and LVS checks. The circuit implemented a logic boolean
        expression with 3 inputs.
    }
    \achievement{
        Skills: \tech{Tanner EDA}, \tech{Calibre}, \tech{CMOS}, \tech{Very-Large-Scale Integration}
    }
}
\experience{Line Following Buggy}{PuzzleThon}{Apr 2023}{Apr 2023}{
    \achievement{
        Programmed Nvidia Jetson Nano for a line-following buggy.
        The algorithm captured front-facing video, processed the image to
        detect line contours, and utilized PD motor control to align the
        line as closely as possible to the middle of the buggy.
    }
    \achievement{
        Skills: \tech{Python}, \tech{Robot Operating System (ROS)}, \tech{Embedded Systems}, \tech{Image Processing}
    }
}
\experience{VHDL Stopwatch}{Coursework}{Nov 2022}{Nov 2022}{
    \achievement{
        Programmed an FPGA in VHDL to implement a functional stopwatch.
    }
    \achievement{
        Skills: \tech{FPGA}, \tech{VHDL}, \tech{Finite State Machine}
    }
}
\experience{Building a Cargo Carrying Drone}{Destination Imagination
    Tournament}{Jan 2018}{Jan 2019}{
    \achievement{
        Built a quadcopter capable of carrying cargo as part of the
        "Destination Imagination" competition Technical category. My team
        earned 1st place in Turkey.
    }\achievement{
        My main responsibility was the cargo carrying. To do that, I have
        coded 2 Arduino boards and connected them via a Bluetooth sensor.
        One Arduino sent a Bluetooth signal to the Arduino on board which
        activated/deactivated the electromagnet on the drone. This allowed
        the drone to carry/drop metal-attached cargo.
    }
    \achievement{
        The skeleton was made by cutting spare metal parts. Flight
        controller hardware pieces were bought, connected, and modded.
    }
    \achievement{
        Skills: \tech{Drones}, \tech{Arduino}, \tech{Microcontrollers},
        \tech{Embedded Systems}, \tech{Python}, \tech{Cabling},
        \tech{Problem Solving} \newline
    }
}


%--------------------------------------------------------------------------------------%
\section{Skills}

\achievement{
    Programming Languages: C, C++, CUDA, SQL, MATLAB with Simulink,
    Mbed, VHDL, Python, Assembly
}
\achievement{
    Software Tools: NI LabVIEW, Tanner EDA Tools, Calibre Verification,
    Altium Designer, Keil uVision
}
\achievement{
    Technical skills: Research, Cleanroom Practices, PVD, Spin-coating,
    Photolithography, Electrical Characterizations \newline
}


%--------------------------------------------------------------------------------------%
\section{Certifications}
\achievement{
    Accelerating CUDA C++ Applications with Concurrent Streams \hfill
    \textsc{Feb 2023}
}
\achievement{
    Fundamentals of Accelerated Computing with CUDA C/C++ \hfill
    \textsc{Jan 2023}
}
\end{document}